Deployable Probabilistic Programming

### 2019-04-16 paper/paper.tex
introduction in progress

The promise of probabilistic programming.

@@

>>>>

	Probabilistic programming \cite{GMR+08,MSP14,WVM14,GS15} represents
	statistical models as programs written in an otherwise
	general programming language that provides syntax for the
	definition and conditioning of random variables. Inference can be
	performed on probabilistic programs to obtain the posterior
	distribution or point estimates of the variables. Inference
	algorithms are provided by the probabilistic programming system,
	and each algorithm is usually applicable to a wide class of
	probabilistic programs in a black box manner.  Inference
	techniques provided by the system back end, such as
	Metropolis-Hastings \cite{WSG11,MSP14,YHG14}, Hamiltonian Monte
	Carlo \cite{SDT14}, expectation propagation \cite{MWG+10},
	extensions of Sequential Monte Carlo \cite{WVM14,MYM+15,PWD+14},
	variational inference~\cite{}, gradient-based
	optimization~\cite{}, and others.

	There are two polar views on the role of probabilistic programming.
	One view is that probabilistic programming is a flexible tool for
	specification of statistical models. Proponents of this view
	probabilistic programming as a tool for data science
	practitioners. A typical work flow consists of data acquisition
	and pre-processing, followed by several iterations of exploratory
	model design and testing of inference algorithms. Once a
	sufficiently robust statistical model is obtained, analysis
	results are post-processed, visualized, and occasionally
	integrated into algorithms of a production software system.

	The other, emerging, view is that probabilistic programming is an
	extension to a regular programming toolbox allowing
	algorithms implemented in general programming languages to
	have learnable parameters. In this view, statistical 
	models are integrated into the software system, and inference
	and optimization take place during data processing, prediction,
	and algorithmic decision making in production.  Probabilistic
	programming code runs unattended, and inference results are an
	integral part of the algorithms.

	In this work we are concerned with the later view on
	probabilistic programming. Our objective is to pave a path to
	deployment of probabilistic programs in production systems,
	promoting a wider adoption of probabilistic programming as a
	flexible tool for ubiquitous statistical inference.

@@

\begin{itemize}
	\item Guidelines for design and implementation of a
		probabilistic programming facility deployable as a part 
		of production software systems.
	\item A reference implementation of deployable probabilistic
		programming facility for the Go programming language.
	\item Design and implementation highlights 
\end{itemize}
